Embedding Dimension of Polyhedral Losses

### 2020-01-25 colt-20/poly-embed.tex
1-d section started, setting section edited

\usepackage{lmodern}
\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
%\usepackage[margin=1.0in]{geometry}

\usepackage{mathtools, amsmath, amssymb, graphicx, verbatim}
%\usepackage{amsthm}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\hypersetup{colorlinks,breaklinks,
	linkcolor=darkblue,urlcolor=darkblue,
	anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

@@

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\dom}{\mathrm{dom}}
\newcommand{\epi}{\text{epi}}
\newcommand{\relint}{\mathrm{relint}}
\newcommand{\prop}[1]{\Gamma[#1]}
\newcommand{\eliccts}{\mathrm{elic}_\mathrm{cts}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}

@@

\section{Introduction}
To do...

\section{Related work and background}

@@

\jessie{A lot fo this is taken from the NeurIPS paper}
Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals_+^{\Y}$, represented as vectors of probabilities.
We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.

As is assumed by~\cite{finocchiaro2019embedding}, we assume the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.

We denote surrogate losses $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$ since we are in the finite outcome setting.

For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
given by $\ellzo(r)_y = \Ind{r \neq y}$, with Bayes risk $\risk{\ellzo}(p) = 1-\max_{y\in\Y} p_y$.
Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = (1-yu)_+$, where $(x)_+ = \max(x,0)$, and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
	A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, hinge loss is polyhedral, whereas logistic loss is not.

We specifically study polyhedral functions in part because they have high-dimensional subgradient sets at points of nondifferentiability, which will be of interest to us later.

\section{Embedding dimension}

\section{1d-characterization}
\label{sec:1d}

\section{Higher dimensions}

\paragraph{Background and notation.}
Recall that we have a loss function $\ell: \R \to \reals^{\Y}_{\geq 0}$, and for any prediction $r \in \R$ of the algorithm, we write $\gamma_r = \{ p : \inprod{p}{\ell(r)} \leq \inprod{p}{\ell(r')} (\forall r')\}$.
We are interested in potential polyhedral surrogates $L: \reals^d \to \reals^{\Y}_{\geq 0}$.
These are associated with embedding points, where $u_r \in \reals^d$ is linked back to the discrete prediction $r$.

To settle the question of whether a consistent surrogate exists in $d$ dimensions, it turns out to be necessary and sufficient to consider the possible sets of subgradients of $L$ at the embedding points.
This is useful in particular because a convex function is minimized at a point if and only if $\vec{0}$ is in its subgradient set at that point.

We will therefore abstract the relevant subgradient sets -- namely, the subgradients of $L$ at the embedding points $u_r$, given observed outcome $y$ -- as bounded, closed polytopes $T^r_y$. (The subgradient sets are bounded closed polytopes because $L$ is polyhedral and defined on all of $\reals^d$.)

\begin{definition}[$\T$, $\T^r$, $D(\T^r)$]
  We use the following notation for a collection of polytopes, with implicit parameter $d$: $\T = \{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$.
  For each fixed $r$, we write $\T^r := \{T^r_y : y \in \Y\}$.

@@

\begin{observation} \label{obs:subdiff-minkowski}
  Let $T^r_y$ be the subgradient set of $L(u_r)_y$.
  Then the subgradient set of the expected loss $\inprod{p}{L(u_r)}$ is $\oplus_p \T^r$.
\end{observation}
\begin{proof}
  \bo{TODO}
\end{proof}
\begin{corollary} \label{cor:minkowski-0-opt}
  If $T^r_y$ is the subgradient set of each $L(u_r)_y$, then $D(\T^r)$ is the set of distributions $p \in \simplex$ for which the embedding point $u_r$ minimizes expected $L$-loss.
\end{corollary}
\begin{proof}
  Any convex function $f$ is minimized at $u$ if and only if $\vec 0$ is a subgradient of $f$ at $u$.
  By Observation \ref{obs:subdiff-minkowski}, $\vec 0$ is a subgradient of $\inprod{p}{L(u_r)}$ if and only if $\vec 0 \in \oplus_p \T^r$, which by definition occurs if and only if $p \in D(\T^r)$.
\end{proof}
This corollary is vital because a discrete loss $\ell$ has a corresponding set of distributions $\gamma_r$ for which $r$ minimizes expected loss; and for calibration, it is necessary that these sets be the same: $\gamma_r = D(\T^r)$.
We expand on this next.

@@

Two conditions are required: \emph{optimality} and \emph{monotonicity}.
Optimality enforces that the surrogate is minimized precisely when and where it should be.
It says that for each discrete prediction $r$ and set of distributions $\gamma_r$ for which it is optimal, there exists a collection of polytopes $\T^r$ (presumably the subgradient sets of $L(u_r)_y$ for each $y$) realizing Corollary \ref{cor:minkowski-0-opt}.
Monotonicity says that these individual polytopes can actually be glued together to form the subgradients of some convex loss function $L$.

@@

The variables are a set of normal vectors $\{v_i \in \reals^d : i \in [k]\}$ and a set of vertices $\{X^j_y \in \reals^d : j \in [\ell], y \in \Y\}$.
These correspond to a (possibly relaxed) halfspace representation and (possibly incomplete) vertex representation of the subgradient polytopes $\T^r$.

@@

  \textbf{Variables:} a matrix $V \in \reals^{k \times d}$, each row representing a normal vector; and a collection of matrices $X^1,\ldots,X^{\ell} \in \reals^{d \times n}$, with $X^j$ intuitively corresponding to $p^j$ with columns $X^j_y$ representing witness points.

  \textbf{Constraints:}
    \begin{align}
      V X^j                     &\leq B    & \text{(pointwise, $\forall j \in [\ell]$)}  \label{eqn:qp-constr-1} \\
      \sum_{y=1}^n p^j(y) X^j_y &= \vec 0  & \text{($\forall j \in [\ell]$)}    \label{eqn:qp-constr-2} 
    \end{align}
\end{definition}

@@

  ($\implies$) 
  By the vertex condition, for each $j \in [\ell]$, there exist witnesses $\{X^j_y \in T^r_y : y \in \Y\}$ satisfying the second constraint of the quadratic program (Inequality \ref{eqn:qp-constr-2}).
  By the halfspace condition, there exist normals $v_1, \dots, v_k$ such that, for all $i$, for all $x \in T^r_y$, $\inprod{v_i}{x} \leq B_{iy}$; in particular, this applies to the above witnesses $X^j_y \in T^r_y$.
  Collecting $v_1,\dots,v_k$ as the columns of $V$, this shows that the first constraint (Inequality \ref{eqn:qp-constr-1}) is satisfied.

  \bigskip
  ($\impliedby$)
  We construct $T^r_y = \conv(\{X^1_y, \ldots, X^{\ell}_y\})$.
  The second constraint of the quadratic program immediately implies the vertex condition.
  Taking $v_1,\dots,v_k$ as the columns of $V$, the first constraint implies that for each $X^j_y$, we have $\inprod{v_i}{X^j_y} \leq B_{iy}$ for all $i,j,y$.
  Any point $x \in T^r_y$ is a convex combination of $X^1_y,\ldots,X^{\ell}_y$, so it satisfies $\inprod{v_i}{x} \leq B_{iy}$.
  This implies the halfspace condition.  % Bo: QED
\end{proof}

>>>>

\usepackage{lmodern}
\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\usepackage{mathtools, verbatim}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\hypersetup{colorlinks,breaklinks,
	linkcolor=darkblue,urlcolor=darkblue,
	anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

@@

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\nonnegreals}{\reals_{\geq 0}}%{\reals_{++}}
\newcommand{\dom}{\mathrm{dom}}
\newcommand{\epi}{\text{epi}}
\newcommand{\relint}{\mathrm{relint}}
\newcommand{\prop}[1]{\Gamma[#1]}
\newcommand{\eliccts}{\mathrm{elic}_\mathrm{cts}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
To do...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Setting}

@@

The base object of study is a \emph{discrete loss function} $\ell: \R \to \nonnegreals^{\Y}$ where $\R$ and $\Y$ are finite sets.
Here $\ell(r)_y$ is the loss of prediction $r \in \R$ (the report space) on $y \in \Y$ (the observation or label space).
For simplicity we let $\Y = [n]$ throughout (where $[n] = \{1,\ldots,n\}$).
The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\nonnegreals^{\Y}$, represented as vectors of probabilities.
We write $p(y)$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
As is assumed by~\cite{finocchiaro2019embedding}, we assume the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.

We denote surrogate losses in dimension $d$ by $L:\reals^d\to\nonnegreals^{\Y}$, with predictions typically written $u\in\reals^d$.
The expected losses when $Y \sim p$ can be written $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
In order to capture how the surrogate corresponds to the original loss, we rely on the following notation from property elicitation literature \bo{cite}: $\gamma_r \subseteq \simplex$ represents those distributions where $r$ minimizes expected loss, i.e. $\gamma_r = \{p : \inprod{p}{\ell(r)} \leq \inprod{p}{\ell(r')} ~ (\forall r' \in \R) \}$.
Similarly, $\Gamma_u = \{ p : \inprod{p}{L(u)} \leq \inprod{p}{L(u')} ~ (\forall u' \in \reals^d) \}$.

For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
given by $\ellzo(r)_y = \Ind{r \neq y}$.%, with Bayes risk $\risk{\ellzo}(p) = 1-\max_{y\in\Y} p_y$.
Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = (1-yu)_+$, where $(x)_+ = \max(x,0)$, and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
	A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral (piecewise linear convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, hinge loss is polyhedral, whereas logistic loss is not.

%We specifically study polyhedral functions in part because they have high-dimensional subgradient sets at points of nondifferentiability, which will be of interest to us later.
Polyhedral losses are motivated partly because they correspond to a natural surrogate construction technique: embedding the discrete predictions $\R$ as points in $\reals^d$.
The key condition is that $r \in \R$ should minimize expected $\ell$-loss if and only if its embedding point minimizes expected surrogate loss.
%
\begin{definition}[Embedding of a loss]
  A loss $L: \reals^d \to \nonnegreals^{\Y}$ \emph{embeds} a loss $\ell: \R \to \nonnegreals^{\Y}$ \emph{in dimension $d$} with \emph{embedding function $\phi: \R \to \reals^d$} if: (i) $\phi$ is injective; (ii) for all $r \in \R$, $\ell(r) = L(\phi(r))$; and (iii) for all $r \in \R$, $\gamma_r = \Gamma_{\phi(r)}$.
  We simply say $L$ \emph{embeds} $\ell$ (in dimension $d$) if some such embedding function exists.
\end{definition}
%
Note that embedding does not immediately imply another important property, calibration.
\begin{definition}[Calibrated surrogate]
  A surrogate loss $L: \reals^d \to \nonnegreals^{\Y}$ and \emph{link function} $\psi: \reals^d \to \R$ are \emph{calibrated} for a loss $\ell: \R \to \nonnegreals^{\Y}$ if for all $p \in \simplex$,
    \[ u \in \argmin_{u' \in \reals^d} \inprod{p}{L(u')} \implies \psi(u) \in \argmin_{r' \in \R} \inprod{p}{\ell(r)} . \]
  We simply say $L$ can be \emph{calibrated} to $\ell$ if such a link function exists.
\end{definition}
Polyhedral surrogates are motivated by the following results.
\begin{theorem}[\cite{finocchiaro2019embedding}] \label{thm:embed-iff-poly}
  If a discrete loss $\ell$ is embedded by some surrogate $L$, then (1) $L$ must be a polyhedral loss; and (2) there exists a link function calibrating $L$ to $\ell$.
\end{theorem}
It therefore suffices for us to investigate when an embedding of $\ell$ exists.
We will get calibration for free.
The next question is what desirable properties would be of a surrogate $L: \reals^d \to \nonnegreals^{\Y}$ (which we know must be polyhedral).
The most immediate is the dimensionality $d$ required.
This is the question investigated in this paper.

\subsection{Embedding dimension}

In this paper, we study the following quantity.
\begin{definition}[Embedding dimension]
  The \emph{embedding dimension} of a discrete loss $\ell: \R \to \nonnegreals^{\Y}$ is the smallest $d$ such that $\ell$ can be embedded into $d$ dimensions, i.e. where there exists a calibrated polyhedral surrogate $L: \reals^d \to \nonnegreals^{\Y}$.
  In this case, we say $\ell$ is \emph{$d$-embeddable}.
\end{definition}

A number of things are already known about embedding dimension.
Many surrogates in the literature provide upper bounds; we highlight in particular the \emph{abstain loss} \bo{cite, describe}.
A known convex-conjugate construction generically embeds any discrete loss on $\Y = [n]$ into $n-1$ dimensions, giving a flat upper bound of $n-1$ on embedding dimension.

Lower bounds exist but are rare.
In particular, a lower bound on the dimensionality of \emph{any} calibrated convex surrogate $L$ implies in particular a lower bound on polyhedral surrogates.
\bo{cite} give such a lower bound via the technique of \emph{feasible subspace dimension}, which is able to e.g. prove that embedding $0-1$ loss on $n$ labels requires dimension $n-1$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{One-dimensional embeddings}
\label{sec:1d}

In this section, we completely characterize when a discrete loss can be embedded into the real line.
Perhaps, surprisingly, we also show that $1$-embeddability is equivalent to the existence of \emph{any} convex calibrated $1$-dimensional surrogate.
We do not expect this fact to extend to higher dimensions, where separating the power of polyhedral from more general convex surrogates is an interesting open problem.

We leverage recent results in \emph{property elicitation}, which formalize the property (or statistic) of a conditional distribution $p$ that is obtained by minimizing loss.
\begin{definition}[Property, finite, level set, elicited]
  A \emph{property} is a function $g: \simplex \to 2^{R}$ where $g(p) \neq \emptyset$ for all $p$.
  It is \emph{finite} if $|\R| < \infty$.
  The \emph{level set} of $r$ is the set $g_r = \{p \in \simplex : r \in g(p)\}$.
  A loss function $f: R \to \nonnegreals^{\Y}$ \emph{elicits} the property if $g(p) = \argmin_{r \in R} \inprod{p}{f(r)}$.
  We assume all properties are non-redundant, i.e. each $g_r$ contains a $p$ not in any other $g_{r'}$.
\end{definition}
In particular, in this paper we write $\gamma$ for the property elicited by $\ell$ and $\Gamma$ for the property elicited by $L$.
For example, $0-1$ loss elicits the mode, which is formalized as a property on report space $\R = \Y$ via $g(p) = \argmax_{y \in \Y} p(y)$.

\bo{This definition actually makes sense if $g$ is not finite; do we want to only define it for finite properties?}
\begin{definition}[Intersection graph, orderable]
  Given a finite property $g: \simplex \to 2^{\R}$, the \emph{intersection graph} has vertices labeled by $\R$ with an edge $(r,r')$ if $g_r \cap g_{r'} \neq \emptyset$.
  A finite property $g$ is \emph{orderable} if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
\end{definition}

%\begin{observation}
%  A property $g$ is orderable if and only if the set $g_r \cap g_{r'}$, for $r \neq r'$, is always the intersection of a hyperplane with the simplex.
%\end{observation}

The main result of this section is Theorem \ref{thm:orderable-1-embed}.
\begin{theorem} \label{thm:orderable-1-embed}
  Given a discrete loss $\ell: \R \to \nonnegreals^{\Y}$, the following are equivalent:
  \begin{enumerate}
    \item The property elicited by $\ell$ is orderable.
    \item $\ell$ is $1$-embeddable.
    \item $\ell$ has some polyhedral calibrated surrogate loss $L: \reals \to \nonnegreals^{\Y}$.
    \item $\ell$ has some convex calibrated surrogate loss $L: \reals \to \nonnegreals^{\Y}$.
  \end{enumerate}
\end{theorem}
This theorem implies that one can directly test if a property is $1$-embeddable via the orderable criterion.
Orderability can be tested using the Bayes risk of $\ell$, a polyhedral function defined by $p \mapsto \max_{r \in \R} \inprod{p}{\ell(r)}$.
A direct approach is to project this function down to the simplex to give the level sets $\gamma_r$ \bo{figure?}.
Another approach is to note that the intersection graph is directly given by finding those pairs $r,r'$ that simultaneously maximize the Bayes risk, i.e. cases where for some $p$, we have $r,r' \in \argmax_{r'' \in \R} \inprod{p}{\ell(r)}$.

\subsection{Proof approach: monotonicity}
\bo{Depending on space, we can give full definitions and proof sketches here, or less.}

The key idea of the proof is to define \emph{monotonicity} of a general property $g: \simplex \to 2^{R}$.
This generalizes orderability to the case where the report space $R$ is not necessarily finite
We show a finite property is orderable if and only if it is monotone.
From the definition of monotonicity, we are able to directly construct a polyhedral surrogate $L$, proving (1) $\implies$ (2) in Theorem \ref{thm:orderable-1-embed}.
The equivalence of embedding and polyhedral surrogates of \cite{finocchiaro2019embedding} (Theorem \ref{thm:embed-iff-poly}) gives (2) $\implies$ (3), and the fact that polyhedral functions are convex gives (3) $\implies$ (4).
Then, we show that monotone properties with report space $\reals$ are precisely those elicited by convex loss functions $L$.
This, along with a result that calibrated link functionss must also be in a sense ``ordered'', proves (4) $\implies$ (1).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Higher dimensions}
\bo{blurb about the purpose of this section and the layout.}

\subsection{Setup: subgradient sets at embedding points.}
%Recall that we have a loss function $\ell: \R \to \reals^{\Y}_{\geq 0}$, and for any prediction $r \in \R$ of the algorithm, we write $\gamma_r = \{ p : \inprod{p}{\ell(r)} \leq \inprod{p}{\ell(r')} (\forall r')\}$.
%We are interested in potential polyhedral surrogates $L: \reals^d \to \reals^{\Y}_{\geq 0}$.
%These are associated with embedding points, where $u_r \in \reals^d$ is linked back to the discrete prediction $r$.

Recall that if $\ell: \R \to \nonnegreals^{\Y}$ is embedded by $L: \reals^d \to \nonnegreals^{\Y}$, then each $r \in \R$ is embedded at some point $u_r \in \reals^d$.
The key to our approach is to study as first-class objects the sets of all subgradients\footnote{Recall that a subgradient of e.g. the convex function $L(\cdot)_y: \reals^d \to \reals$ at a point $u$ is a vector $v \in \reals^d$ such that $L(u') \geq L(u) + \inprod{v}{u'-u}$ for all $u'$. The set of subgradients at $u$ is sometimes called the subdifferential.} of $L$ at these embedding points.
To settle the question of whether a consistent surrogate exists in $d$ dimensions, it surprisingly turns out to be necessary and sufficient to consider conditions on these sets alone.
In particular, we use heavily that a convex function is minimized at a point if and only if $\vec{0}$ is in its subgradient set at that point.

Therefore, we abstract to consider collections of sets $T^r_y$, which aspire to be the subgradient sets of a calibrated polyhedral surrogate $L(\cdot)_y$ at $u_r$.
Note that if $L(\cdot)_y$ is a polyhedral function on $\reals^d$, then all of its subgradient sets are (bounded) closed polytopes.\bo{cite}

\begin{definition}[$\T$, $\T^r$, $D(\T^r)$]
  We use the following notation for a collection of closed polytopes, with implicit parameter $d$: $\T = \{T^r_y \subseteq \reals^d : r \in \R, y \in \Y\}$.
  For each fixed $r$, we write $\T^r := \{T^r_y : y \in \Y\}$.

@@

The importance of the $p$-weighted Minkowski sum and of $D(\T^r)$ are that they capture the distributions $p$ for which $u_r$ minimizes expected loss, assuming that $\T$ correspond to some polyhedral $L$.
\begin{proposition} \label{prop:minkowski-0-opt}
  If $T^r_y$ is the subgradient set of each $L(u_r)_y$, then $D(\T^r)$ is the set of distributions $p \in \simplex$ for which the embedding point $u_r$ minimizes expected $L$-loss.
\end{proposition}
\begin{proof}
  Any convex function $f$ is minimized at $u$ if and only if $\vec 0$ is a subgradient of $f$ at $u$.
  Let $f(u) = \inprod{p}{L(u)}$.
  Then the subgradient set of $f$ at $u$ is $\oplus_p \T^r$.
  This follows from the basic properties that if $f_1,f_2$ are convex with subgradient sets $T_1,T_2$ at $u$, then $\alpha f_1$ has subgradient set $\alpha T_1$ and $f_1 + f_2$ has subgradient set $T_1 \oplus T_2$, the Minkowski sum.
  So $\vec 0$ is a subgradient of $\inprod{p}{L(u_r)}$ if and only if $\vec 0 \in \oplus_p \T^r$, which by definition occurs if and only if $p \in D(\T^r)$.
\end{proof}
This fact will be vital for characterizing when $\ell$ is correctly embedded by some $L$ whose subgradient sets are $\T$.
We leverage it next.

@@

Two conditions are required: \emph{optimality} and \emph{monotonicity}.
Optimality enforces that the surrogate is minimized precisely when and where it should be.
It says that for each discrete prediction $r$ and set of distributions $\gamma_r$ for which it is optimal, there exists a collection of polytopes $\T^r$ (presumably the subgradient sets of $L(u_r)_y$ for each $y$) realizing Proposition \ref{prop:minkowski-0-opt}.
Monotonicity says that these individual polytopes can actually be glued together to form the subgradients of some convex loss function $L$.

@@

The variables are a set of normal vectors $\{v_i \in \reals^d : i \in [k]\}$ and a set of vertices $\{x^j_y \in \reals^d : j \in [\ell], y \in \Y\}$.
These correspond to a (possibly relaxed) halfspace representation and (possibly incomplete) vertex representation of the subgradient polytopes $\T^r$.

@@

  \textbf{Variables:} a matrix $V \in \reals^{k \times d}$, each row representing a normal vector; and a collection of matrices $X^1,\ldots,X^{\ell} \in \reals^{d \times n}$, with $X^j$ intuitively corresponding to $p^j$ with columns $x^j_y$ representing witness points.

  \textbf{Constraints:}
    \begin{align}
      V X^j                     &\leq B    & \text{(pointwise, $\forall j \in [\ell]$)}  \label{eqn:qp-constr-1} \\
      \sum_{y=1}^n p^j(y) x^j_y &= \vec 0  & \text{($\forall j \in [\ell]$)}    \label{eqn:qp-constr-2} 
    \end{align}
\end{definition}

@@

  ($\implies$) 
  By the vertex condition, for each $j \in [\ell]$, there exist witnesses $\{x^j_y \in T^r_y : y \in \Y\}$ satisfying the second constraint of the quadratic program (Inequality \ref{eqn:qp-constr-2}).
  By the halfspace condition, there exist normals $v_1, \dots, v_k$ such that, for all $i$, for all $x \in T^r_y$, $\inprod{v_i}{x} \leq B_{iy}$; in particular, this applies to the above witnesses $x^j_y \in T^r_y$.
  Collecting $v_1,\dots,v_k$ as the columns of $V$, this shows that the first constraint (Inequality \ref{eqn:qp-constr-1}) is satisfied.

  \bigskip
  ($\impliedby$)
  We construct $T^r_y = \conv(\{x^1_y, \ldots, x^{\ell}_y\})$.
  The second constraint of the quadratic program immediately implies the vertex condition.
  Taking $v_1,\dots,v_k$ as the columns of $V$, the first constraint implies that for each $x^j_y$, we have $\inprod{v_i}{x^j_y} \leq B_{iy}$ for all $i,j,y$.
  Any point $x \in T^r_y$ is a convex combination of $x^1_y,\ldots,x^{\ell}_y$, so it satisfies $\inprod{v_i}{x} \leq B_{iy}$.
  This implies the halfspace condition.  % Bo: QED
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Examples}
